\documentclass[11pt,a4paper,sans,english]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.8,a4paper,top=0.75cm,bmargin=.75cm,footnotesep=.5cm]{geometry}
\recomputelengths 
\usepackage{babel}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Bret}
\familyname{Koppel}
%\title{Resumé title}                               % optional, remove/comment the line if not wanted
\address{506 Hill St. Ft. Thomas, KY 41075}{}{}         % optional, remove/comment the line if not wanted; the "country" arguments can be omitted or provided empty
\mobile{513-252-2493}                          % optional, remove/comment the line if not wanted
%\phone{phone number}                           % optional, remove/comment the line if not wanted
%\fax{fax number}                             % optional, remove/comment the line if not wanted

\email{bret@bretkoppel.com}                               % optional, remove/comment the line if not wanted
\social[twitter]{bretkoppel}
\social[linkedin]{bretkoppel}
\homepage{bretkoppel.com}                         % optional, remove/comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove/comment the line if not wanted
% \photo[64pt][0.4pt]{picture}                       % optional, uncomment the line if wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{some quote}                                 % optional, remove/comment the line if not wanted
%
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-6mm}
%\section{Master thesis}
%\cvitem{title}{Title}
%\cvitem{supervisors}{Supervisors}
%\cvitem{description}{Short thesis abstract}
\section{Experience}
%\subsection{Vocational}
\cventry{July 11--Present}{Co-Founder}{KIS Group}{kisgroup.com}{}{Sole developer and designer}
\cvlistitem{Built site using ASP .NET MVC, Javascript, and SQL Server}
\cvlistitem{Developed custom Lucene-driven video relationship system}
%\cvlistitem{Worked with third party vendors and freelancers on specific aspects}
\cvlistitem{Managed a team of four to develop an efficient content production flow}
\cventry{October 06--Present}{Senior Web Application Developer}{Burke, Inc.}{burke.com}{}{Full stack developer gathering and implementing custom reporting needs for clients at Fortune 50 companies.}
\cvlistitem{Gathered requirements and produced mock-ups of potential solutions to determine best fit for clients.}
\cvlistitem{Developed database, server-side, and client-side solutions to report client data through a custom SQL Server/JavaScript/ASP.NET data visualization product I helped to architect.}
\cvlistitem{Reduced costly errors and improved client experience by automating developer builds, introducing unit testing, and reducing the amount of data transferred while navigating our data visualization solution.}
\cvlistitem{Drastically cut setup, deployment, and maintenance costs of our solution by building a custom data retrieval and transformation process to bridge the gap between our survey environment and our data visualization solution.}
\cvlistitem{Lead small teams in the development of surveys and new features.}
%\cventry{}{}{Independent}{maradyer.com}{}{}
%\cvlistitem{Worked with designer and client to finalize a design}
%\cvlistitem{Built site using Ruby, Middleman, and Javascript}
%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines}
%\section{Languages}
%\cvitemwithcomment{C\#(ASP .NET MVC, WebForms)}{Unit Testing(nUnit, Moq); WCF and WebAPI services; oAuth integration; Performance analysis}{Comment}
%\cvitemwithcomment{T-SQL(SQL Server)}{Database and table design; Stored procedure design; Security and role assignment; Performance, index, and query plan analysis}{Comment}
%\cvitemwithcomment{Language 3}{Skill level}{Comment}
\section{Computer Skills(Professional)}
\cvitem{C\#, ASP .NET MVC/WebForms}{Unit Testing(nUnit, Moq); Performance
 analysis; WCF and WebAPI services; Third party library integration(oAuth, SAAS, etc.); Light IIS administration}
\cvitem{Javascript}{jQuery, Bootstrap, Loaders(YepNope, Lab, etc.), Templating(Mustache, Hogan, etc.) }
\cvitem{SQL Server}{Database and table design; Stored procedure design; Security and role assignment; Performance, index, and query plan analysis}
\cvitem{Balsamiq}{Complex mock-ups of requested features for stakeholder sign-off}
%\cvdoubleitem{Category 1}{Comment}{Category 4}{Comment}
%\cvdoubleitem{Category 2}{Comment}{Category 5}{Comment}
%\cvdoubleitem{Category 3}{Comment}{Category 6}{Comment}
\section{Computer Skills(Hobbyist)}
\cvitemwithcomment{Ruby}{Exploring dynamic programming paradigms and DSLs}{Rails, Middleman, Chef}
\cvitem{Clojure}{Exploring functional / lisp programming paradigms and parallelism}
%\cvitem{Machine Learning}{Analyzing large data sets to find common items and extrapolating findings to new data}
\section{Community Involvement}
\cvitem{Givecamp(southwestohiogivecamp.org, columbusgivecamp.org)}{Helped small, non-profit organizations upgrade their internal and external technology by donating weekends}
\cvitem{Conferences(Codemash, Central Ohio Day of .NET)}{Annual conference attendee since 2011}
%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem{Item 3}
%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5}
%\cvlistdoubleitem{Item 3}{Item 6}
\section{Education}
\cventry{2001--2005}{BS, Computer Systems Analysis}{Miami University}{Oxford, OH}{}{}  % arguments 3 to 6 can be left empty
%\vspace*{-5mm}
\section{References}
\cventry{}{}{Available upon request}{}{}{}  %
%\cvitem{Available upon request}{}
%\begin{cvcolumns}
%  \cvcolumn{Category 1}{Comment}
%  \cvcolumn{Category 2}{Comment}
%  \cvcolumn{Category 3}{Comment}
%\end{cvcolumns}
\clearpage
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Company Recruitment team}{Company's name\\Street address\\Zip Code City}
\date{Date}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}
\enclosure{enclosures}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle
I'm a full stack **ASP.NET / SQL Server** web engineer looking for a position where I can make a difference... Working at (company), where I'll have the opportunity to (something) sounds like a great place to... (Not good)

Although I'm now looking for a position where I can make a difference on a larger scale, I demonstrate my commitment each day to (improving internal things) in my current role. Early in my tenure I was noticed for my passion to improve the lives of my teammates and those who interact with our department. I made a name for myself by automating previously manual processes and revising inefficient ones. When one department's SQL work was slowing down another, I was the one getting phone calls to see if I could provide insight and relief. Soon I was promoted to web development where I brought that same passion to our team's internal tooling: setting up automated builds; introducing the group to unit testing; and automating long-running "watch and wait" processes. When (one of our company's second in commands) needed somebody to do this more officially, he specifically sought me out to offer me the opportunity. 

I'm also committed to making a difference outside the office. I regularly participate in Givecamps - 48 hour weekend code-a-thons in which I solve a technical need for a charity who can't afford to have the work done. (flesh this out)

I'm excited to bring my commitment to improvement to (your company) and look forward to hearing from you.
\makeletterclosing
\end{document}
